---
title: "Carseats"
output: html_document
---

This document is an example of regression analysis with data where there are qualitative predictors.  It utilizes the Carseats data from the ISLR library.

```{r}
library(ISLR)
fix(Carseats)
names(Carseats)
```

```{r}
hist(Carseats$Sales)
```

We'll fit a linear model using all of the available predictors, plus two interaction terms:  Income-Advertising and Price-Age.

```{r}
lm.fit = lm(Sales~.+Income:Advertising+Price:Age, data=Carseats)
summary(lm.fit)
```
This model has 9 predictors with significant Beta estimates.  Also, the overall fit of the model (based on R-squared) is quite good.

Note that the qualitative variable ShelveLoc has 3 levels (Good, Medium, and Bad) has been automatically coded as 2 binary dummy variables: ShelveLocGood and ShelveLocMedium.  ShelveLocBad is indicated by both of the aforementioned variables having values of zero.

We can investigate the encoding using the "contrasts"" function.
```{r}
contrasts(Carseats$ShelveLoc)
```
Next we check the residuals of the fit :
```{r}
par(mfrow=c(2,2))
plot(lm.fit2)
```

